Cellct analysis

### 2019-11-02 code/cellcount.Rmd
minor changes

morpho_order <- c("Green cell",
                  "Sanguina 'citrine'",
                  "Sanguina nivaloides",
                  "Sanguina nivaloides 'turret'",
                  "Green cell",
                  "Chlainomonas",
                  "Chloromonas krienitzii",
                  "Chloromonas cf. brevispina",
                  "Chloromonas cf. nivalis",
                  "Chloromonas 'spiny'",
                  "Chloromonas 'oval'",
                  "Chloromonas 'zuke'"
                  )

@@

ggplot(p, aes(y=alias %>% fct_reorder(elev_m), 
              x=morpho_sp)) +
  geom_tile(aes(alpha = percent_of_sample, fill = morpho_sp)) + # color = "white" %>% fct_reorder(morpho_order)
  labs(title="Cell count relative abundance", x="Cell morphology", y= "Sample ID", fill = "Cell morphology", alpha="Relative abundance") +
  guides(fill=F) +
  scale_alpha(range = c(0.1, 1)) +
  my_theme
```

>>>>

morpho_order <- c("Green cell",
                  "Sanguina 'citrine'",
                  "Sanguina nivaloides",
                  "Sanguina nivaloides 'ruby'",
                  "Green cell",
                  "Chlainomonas",
                  "Chloromonas krienitzii",
                  "Chloromonas cf. brevispina",
                  "Chloromonas cf. nivalis",
                  "Chloromonas 'spiny'",
                  "Chloromonas 'oval'",
                  "Chloromonas 'zuke'"
                  )

@@

ggplot(p, aes(y=alias %>% fct_reorder(elev_m), 
              x=morpho_sp)) +
  geom_tile(aes(alpha = percent_of_sample, fill = morpho_sp)) + # color = "white" %>% fct_reorder(morpho_order)
  labs(x="Cell morphology", y= "Sample ID", fill = "Cell morphology", alpha="Relative abundance") +
  guides(fill=F) +
  scale_alpha(range = c(0.1, 1)) +
  my_theme
```
